---
title: "First Pass"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("plm")
library("pglm")
library("scales")
library("stargazer")
library("stringr")
library("tidyverse")
library("viridis")

sumn  <- function(x) ifelse(all(is.na(x)), NA, sum(x, na.rm = T))
meann <- function(x) ifelse(all(is.na(x)), NA, mean(x, na.rm = T))
varn  <- function(x) ifelse(all(is.na(x)), NA, var(x, na.rm = T))
inv_hypersine <- function(x){
  log(x + (x^2 + 1)^0.5)
}

ddays   <- read_rds("../1-tidy/ddays/ddays.rds")
ddays_p <- pdata.frame(ddays, c("fips", "year"))

# Regressions
dd_formula <- formula(inv_hypersine(b_rate) ~ dday_good + dday34 + 
                        prec + I(prec^2) + I(covered_impute/1000) + I(subsidy/1000) + I(indemnity/1000))
controls_formula <- update(dd_formula, . ~ . +
                              I(farmland_val_per_acre_interp/1000) +
                              lag(I(farmland_val_per_acre_interp/1000)) +
                              # the net_cash_per_interp variable is highly skewed
                              #net_cash_per_interp + lag(net_cash_per_interp) +
                              I(farms_interp/1000) +
                              livestock_share + pct_irrigated +
                              unemp_rate + I(total_branches/1000))

```

# Generic Results

Dependent variables are either the chapter 12 bankruptcy rate, the 90+ day delinquency rate of production loans, or the 90+ day delinquency rate of farmland loans. Chapter 12 data begin in 1990 while the delinquency rates begin in 1994.

## Panel fixed effects and with controls

Fixed effects for both county and year.

```{r twoways-effects, results = "asis"}
# Regressions
brate_twoways <- plm(dd_formula, ddays_p, effect = "twoways")
brate_twoways_c <- plm(controls_formula, ddays_p, effect = "twoways")

agl_twoways   <- plm(update(dd_formula, inv_hypersine(agloan_d_rate) ~ .),
                  ddays_p, effect = "twoways")
agl_twoways_c   <- plm(update(controls_formula, inv_hypersine(agloan_d_rate) ~ .),
                       ddays_p, effect = "twoways")

agl_re_twoways <- plm(update(dd_formula, inv_hypersine(agloan_re_d_rate) ~ .),
                   ddays_p, effect = "twoways")
agl_re_twoways_c <- plm(update(controls_formula, inv_hypersine(agloan_re_d_rate) ~ .),
                     ddays_p, effect = "twoways")

# Tables

stargazer(brate_twoways, brate_twoways_c,
          agl_twoways, agl_twoways_c,
          agl_re_twoways,  agl_re_twoways_c,
          # agl_all_twoways, agl_all_twoways_c,
          se = list(sqrt(diag(vcovHC(brate_twoways))),
                    sqrt(diag(vcovHC(brate_twoways_c))),
                    sqrt(diag(vcovHC(agl_twoways))),
                    sqrt(diag(vcovHC(agl_twoways_c))),
                    sqrt(diag(vcovHC(agl_re_twoways))),
                    sqrt(diag(vcovHC(agl_re_twoways_c)))),
          
          type = "html",
          font.size = "scriptsize", no.space = TRUE,
          dep.var.caption = "Inverse Hyperbolic Sine of",
          dep.var.labels.include = FALSE,
          column.labels = c("Ch. 12 Rate", "Ch. 12 Rate",
                            "Production Delinq.", "Production Delinq.",
                            "Farmland Delinq.", "Farmland Delinq."),
          
          # omit = "farms_interp",
          omit.stat = c("adj.rsq", "f"),
          # covariate.labels = c("Good DDs", "Extreme DDs", "Rain",
          #                      "Rain Squared", "Value of Farmland",
          #                      "Lagged Value of Farmland",
          #                      "Number of Farms",
          #                      "Share of Livestock",
          #                      "Percent Irrigated",
          #                      "Unemployment Rate",
          #                      "Total Branches"),
          add.lines = list(c("County FEs", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
                           c("Year FEs", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")),
          header = FALSE, column.sep.width = "1pt",
          notes = paste0("Robust standard errors, p<0.1 <sup>+</sup>; p<0.05",
                         " <sup>++</sup>; p<0.01 <sup>+++</sup>"),
          notes.append = FALSE,
          # keep.stat = c("n", "ll"),
          # label = "tab:robust-regs",
          title = "County Fixed Effects Results")

```


## County fixed and with controls

Only county fixed effects, the year fixed effects are omitted.

```{r ind-effects, results = "asis"}
brate_ind <- plm(dd_formula, ddays_p, effect = "individual")
brate_ind_c <- plm(controls_formula, ddays_p, effect = "individual")

agl_ind   <- plm(update(dd_formula, inv_hypersine(agloan_d_rate) ~ .),
                 ddays_p, effect = "individual")
agl_ind_c   <- plm(update(controls_formula, inv_hypersine(agloan_d_rate) ~ .),
                 ddays_p, effect = "individual")

agl_re_ind <- plm(update(dd_formula, inv_hypersine(agloan_re_d_rate) ~ .),
                  ddays_p, effect = "individual")
agl_re_ind_c <- plm(update(controls_formula, inv_hypersine(agloan_re_d_rate) ~ .),
                  ddays_p, effect = "individual")

# Tables

stargazer(brate_ind, brate_ind_c,
          agl_ind, agl_ind_c,
          agl_re_ind,  agl_re_ind_c,
          se = list(sqrt(diag(vcovHC(brate_ind))),
                    sqrt(diag(vcovHC(brate_ind_c))),
                    sqrt(diag(vcovHC(agl_ind))),
                    sqrt(diag(vcovHC(agl_ind_c))),
                    sqrt(diag(vcovHC(agl_re_ind))),
                    sqrt(diag(vcovHC(agl_re_ind_c)))),
          
                    type = "html",
          font.size = "scriptsize", no.space = TRUE,
          dep.var.caption = "Inverse Hyperbolic Sine of",
          dep.var.labels.include = FALSE,
          column.labels = c("Ch. 12 Rate", "Ch. 12 Rate",
                            "Production Delinq.", "Production Delinq.",
                            "Farmland Delinq.", "Farmland Delinq."),
          
          # omit = "farms_interp",
          omit.stat = c("adj.rsq", "f"),
          # covariate.labels = c("Good DDs", "Extreme DDs", "Rain",
          #                      "Rain Squared", "Value of Farmland",
          #                      "Lagged Value of Farmland",
          #                      "Number of Farms",
          #                      "Share of Livestock",
          #                      "Percent Irrigated",
          #                      "Unemployment Rate",
          #                      "Total Branches"),
          add.lines = list(c("County FEs", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
                           c("Year FEs", "No", "No", "No", "No", "No", "No")),
          header = FALSE, column.sep.width = "1pt",
          notes = paste0("Robust standard errors, p<0.1 <sup>+</sup>; p<0.05",
                         " <sup>++</sup>; p<0.01 <sup>+++</sup>"),
          notes.append = FALSE,
          # keep.stat = c("n", "ll"),
          # label = "tab:robust-regs",
          title = "County Fixed Effects Results")
```


## Time fixed and with controls

Only time fixed effects, no county fixed effects.

```{r time-effects, results = "asis"}
brate_time <- plm(dd_formula, ddays_p, effect = "time")
brate_time_c <- plm(controls_formula, ddays_p, effect = "time")

agl_time   <- plm(update(dd_formula, inv_hypersine(agloan_d_rate) ~ .),
                 ddays_p, effect = "time")
agl_time_c   <- plm(update(controls_formula, inv_hypersine(agloan_d_rate) ~ .),
                   ddays_p, effect = "time")

agl_re_time <- plm(update(dd_formula, inv_hypersine(agloan_re_d_rate) ~ .),
                  ddays_p, effect = "time")
agl_re_time_c <- plm(update(controls_formula, inv_hypersine(agloan_re_d_rate) ~ .),
                    ddays_p, effect = "time")

# Tables
stargazer(brate_time, brate_time_c,
          agl_time, agl_time_c,
          agl_re_time,  agl_re_time_c,
          # agl_all_time, agl_all_time_c,
          se = list(sqrt(diag(vcovHC(brate_time))),
                    sqrt(diag(vcovHC(brate_time_c))),
                    sqrt(diag(vcovHC(agl_time))),
                    sqrt(diag(vcovHC(agl_time_c))),
                    sqrt(diag(vcovHC(agl_re_time))),
                    sqrt(diag(vcovHC(agl_re_time_c)))),
          
          type = "html",
          font.size = "scriptsize", no.space = TRUE,
          dep.var.caption = "Inverse Hyperbolic Sine of",
          dep.var.labels.include = FALSE,
          column.labels = c("Ch. 12 Rate", "Ch. 12 Rate",
                            "Production Delinq.", "Production Delinq.",
                            "Farmland Delinq.", "Farmland Delinq."),
          
          # omit = "farms_interp",
          omit.stat = c("adj.rsq", "f"),
          # covariate.labels = c("Good DDs", "Extreme DDs", "Rain",
          #                      "Rain Squared", "Value of Farmland",
          #                      "Lagged Value of Farmland",
          #                      "Number of Farms",
          #                      "Share of Livestock",
          #                      "Percent Irrigated",
          #                      "Unemployment Rate",
          #                      "Total Branches"),
          add.lines = list(c("County FEs", "No", "No", "No", "No", "No", "No"),
                           c("Year FEs", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")),
          header = FALSE, column.sep.width = "1pt",
          notes = paste0("Robust standard errors, p<0.1 <sup>+</sup>; p<0.05",
                         " <sup>++</sup>; p<0.01 <sup>+++</sup>"),
          notes.append = FALSE,
          # keep.stat = c("n", "ll"),
          # label = "tab:robust-regs",
          title = "Time Fixed Effects Results")
```

